---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# plotGenStruct

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/aj2duncan/plotGenStruct.svg?branch=master)](https://travis-ci.com/aj2duncan/plotGenStruct)
<!-- badges: end -->

The goal of plotGenStruct is to assist with plotting clustered genetic STRUCTURE datasets using the [ggplot2](https://ggplot2.tidyverse.org/) package. Data is automatically sorted into clusters and several palettes can be easily chosen.

## Installation

At present the package can only be installed from github with:

``` r
# install.packages("devtools")
devtools::install_github("aj2duncan/plotGenStruct")
```
## Plotting Data

Existing STRUCTURE data can be plotted using the function `struc_plot()`. If you don't have any data to hand then some random data can be generated using the `create_sruc_data()` function

This is a basic example which shows you how to solve a common problem:

```{r creating}
library(plotGenStruct)
create_struc_data()
```

To see what the reordered data looks like we can use `struc_reorder()`.

```{r reorder}
struc_reorder(create_struc_data())
```

Finally we can plot the data. 

```{r plot1}
struc_plot(create_struc_data())
```

### Different Palettes

You can also specify different palettes which is just a short cut to several of the `scale_fill_*()` functions from [ggplot2](https://ggplot2.tidyverse.org/).

```{r plot2}
struc_plot(create_struc_data(), fill_pal = "viridis")
```

This includes a custom palette. Here we also specify only two clusters.

```{r plot3}
# custom palette
struc_plot(create_struc_data(num_clusters = 2), 
           fill_pal = "custom", values = c("blue", "red"))
```

